Draft_Application_Stochastic_Volatility

### 2021-08-10 Real Dataset SV.Rmd
Aggiornate funzioni grafici

Filtplot1<-function(dataframe,title){
  mean=sv_bpf1
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=y1, col="Observations", linetype="Observations"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Observations" = "gray",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Observations" = 1,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot2<-function(dataframe,title){
  mean=sv_gpfopt1
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=y1, col="Observations", linetype="Observations"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Observations" = "gray",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Observations" = 1,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot3<-function(dataframe,title){
  mean=sv_apf1
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=y1, col="Observations", linetype="Observations"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Observations" = "gray",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Observations" = 1,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot4<-function(dataframe,title){
  mean=sv_lw1
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=y1, col="Observations", linetype="Observations"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Observations" = "gray",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Observations" = 1,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot5<-function(dataframe,title){
  mean=sv_bapf1
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=y1, col="Observations", linetype="Observations"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Observations" = "gray",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Observations" = 1,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot6<-function(dataframe,title){
  mean=sv_sis1
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

@@

plotobs1<-Filtplot1(dfsv1,"Bootstrap Particle Filter SP500")
plotobs2<-Filtplot2(dfsv2,"Opt Ker Guided Particle Filter SP500")
plotobs3<-Filtplot3(dfsv3,"Auxiliary Particle Filter SP500")
plotobs4<-Filtplot4(dfsv4,"Liu and West Filter SP500")
plotobs5<-Filtplot5(dfsv5,"Always Resampling SP500")
plotobs6<-Filtplot6(dfsv6,"No Resampling SP500")

@@

Filtplot7<-function(dataframe,title){
  mean=sv_bpf2
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=y2, col="Observations", linetype="Observations"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Observations" = "gray",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Observations" = 1,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot8<-function(dataframe,title){
  mean=sv_gpfopt2
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=y2, col="Observations", linetype="Observations"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Observations" = "gray",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Observations" = 1,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot9<-function(dataframe,title){
  mean=sv_apf2
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=y2, col="Observations", linetype="Observations"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Observations" = "gray",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Observations" = 1,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot10<-function(dataframe,title){
  mean=sv_lw2
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=y2, col="Observations", linetype="Observations"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Observations" = "gray",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Observations" = 1,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot11<-function(dataframe,title){
  mean=sv_bapf2
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=y2, col="Observations", linetype="Observations"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Observations" = "gray",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Observations" = 1,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot12<-function(dataframe,title){
  mean=sv_sis2
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

@@

plotobs7<-Filtplot7(dfsv7,"Bootstrap Particle Filter STOXX50E")
plotobs8<-Filtplot8(dfsv8,"Opt Ker Guided Particle Filter STOXX50E")
plotobs9<-Filtplot9(dfsv9,"Auxiliary Particle Filter STOXX50E")
plotobs10<-Filtplot10(dfsv10,"Liu and West Filter STOXX50E")
plotobs11<-Filtplot11(dfsv11,"Always Resampling STOXX50E")
plotobs12<-Filtplot12(dfsv12,"No Resampling STOXX50E")

@@

Filtplot13<-function(dataframe,title){
  mean=sv_bpf3
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=y3, col="Observations", linetype="Observations"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Observations" = "gray",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Observations" = 1,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot14<-function(dataframe,title){
  mean=sv_gpfopt3
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=y3, col="Observations", linetype="Observations"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Observations" = "gray",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Observations" = 1,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot15<-function(dataframe,title){
  mean=sv_apf3
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=y3, col="Observations", linetype="Observations"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Observations" = "gray",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Observations" = 1,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot16<-function(dataframe,title){
  mean=sv_lw3
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=y3, col="Observations", linetype="Observations"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Observations" = "gray",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Observations" = 1,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot17<-function(dataframe,title){
  mean=sv_bapf3
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=y3, col="Observations", linetype="Observations"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Observations" = "gray",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Observations" = 1,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot18<-function(dataframe,title){
  mean=sv_sis3
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

@@

plotobs13<-Filtplot13(dfsv13,"Bootstrap Particle Filter DJI")
plotobs14<-Filtplot14(dfsv14,"Opt Ker Guided Particle Filter DJI")
plotobs15<-Filtplot15(dfsv15,"Auxiliary Particle Filter DJI")
plotobs16<-Filtplot16(dfsv16,"Liu and West Filter DJI")
plotobs17<-Filtplot17(dfsv17,"Always Resampling DJI")
plotobs18<-Filtplot18(dfsv18,"No Resampling DJI")

@@

Filtplot1<-function(dataframe,title){
  mean=sv_bpf1
  sd=sv_bpf1sd
  dataframe<-data.frame(dataframe,mean)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=btbenchmark, col="BT benchmark", linetype="BT benchmark"))+
    geom_line(aes(y=mean, col="Filtered States", linetype="Filtered States"))+
    geom_ribbon(aes(ymin = mean -1.96*sd, ymax = mean +1.96*sd),
                fill="red",alpha=0.16) +
    scale_color_manual("",
                       values=c("BT benchmark" = "black",
                                "Filtered States"= "red"))+
    scale_linetype_manual("",
                          values=c("BT benchmark" = 1,
                                   "Filtered States"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot2<-function(dataframe,title){
  mean=sv_gpfopt1
  sd=sv_gpfopt1sd
  dataframe<-data.frame(dataframe,mean)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=btbenchmark, col="BT benchmark", linetype="BT benchmark"))+
    geom_line(aes(y=mean, col="Filtered States", linetype="Filtered States"))+
    geom_ribbon(aes(ymin = mean -1.96*sd, ymax = mean +1.96*sd),
                fill="red",alpha=0.16) +
    scale_color_manual("",
                       values=c("BT benchmark" = "black",
                                "Filtered States"= "red"))+
    scale_linetype_manual("",
                          values=c("BT benchmark" = 1,
                                   "Filtered States"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot3<-function(dataframe,title){
  mean=sv_apf1
  sd=sv_apf1sd
  dataframe<-data.frame(dataframe,mean)

@@

Filtplot5<-function(dataframe,title){
  mean=sv_bapf1
  sd=sv_bapf1sd
  dataframe<-data.frame(dataframe,mean)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=btbenchmark, col="BT benchmark", linetype="BT benchmark"))+
    geom_line(aes(y=mean, col="Filtered States", linetype="Filtered States"))+
    geom_ribbon(aes(ymin = mean -1.96*sd, ymax = mean +1.96*sd),
                fill="red",alpha=0.16) +
    scale_color_manual("",
                       values=c("BT benchmark" = "black",
                                "Filtered States"= "red"))+
    scale_linetype_manual("",
                          values=c("BT benchmark" = 1,
                                   "Filtered States"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot6<-function(dataframe,title){
  mean=sv_sis1
  sd=sv_sis1sd
  dataframe<-data.frame(dataframe,mean)

plotcomp1<-Filtplot1(dfsv1,"Bootstrap Particle Filter SP500")
plotcomp2<-Filtplot2(dfsv2,"Opt Ker Guided Particle Filter SP500")
plotcomp3<-Filtplot3(dfsv3,"Auxiliary Particle Filter SP500")
plotcomp5<-Filtplot5(dfsv5,"Always Resampling SP500")
plotcomp6<-Filtplot6(dfsv6,"No Resampling SP500")

@@

Filtplot1<-function(dataframe,title){
  mean=sv_bpf1
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=realisedx1, col="Proxy", linetype="Proxy"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Proxy" = "black",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Proxy" = 3,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot2<-function(dataframe,title){
  mean=sv_gpfopt1
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=realisedx1, col="Proxy", linetype="Proxy"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Proxy" = "black",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Proxy" = 3,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot3<-function(dataframe,title){
  mean=sv_apf1
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=realisedx1, col="Proxy", linetype="Proxy"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Proxy" = "black",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Proxy" = 3,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot4<-function(dataframe,title){
  mean=sv_lw1
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=realisedx1, col="Proxy", linetype="Proxy"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Proxy" = "black",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Proxy" = 3,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot5<-function(dataframe,title){
  mean=sv_bapf1
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=realisedx1, col="Proxy", linetype="Proxy"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Proxy" = "black",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Proxy" = 3,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot6<-function(dataframe,title){
  mean=sv_sis1
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=realisedx1, col="Proxy", linetype="Proxy"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Proxy" = "black",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Proxy" = 3,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}

plotproxy1<-Filtplot1(dfsv1,"Bootstrap Particle Filter SP500")
plotproxy2<-Filtplot2(dfsv2,"Opt Ker Guided Particle Filter SP500")
plotproxy3<-Filtplot3(dfsv3,"Auxiliary Particle Filter SP500")
plotproxy4<-Filtplot4(dfsv4,"Liu and West Filter SP500")
plotproxy5<-Filtplot5(dfsv5,"Always Resampling SP500")
plotproxy6<-Filtplot6(dfsv6,"No Resampling SP500")

@@

Filtplot7<-function(dataframe,title){
  mean=sv_bpf2
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=realisedx2, col="Proxy", linetype="Proxy"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Proxy" = "black",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Proxy" = 3,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot8<-function(dataframe,title){
  mean=sv_gpfopt2
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=realisedx2, col="Proxy", linetype="Proxy"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Proxy" = "black",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Proxy" = 3,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot9<-function(dataframe,title){
  mean=sv_apf2
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=realisedx2, col="Proxy", linetype="Proxy"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Proxy" = "black",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Proxy" = 3,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot10<-function(dataframe,title){
  mean=sv_lw2
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=realisedx2, col="Proxy", linetype="Proxy"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Proxy" = "black",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Proxy" = 3,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}
Filtplot11<-function(dataframe,title){
  mean=sv_bapf2
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

>>>>

Filtplot1<-function(dataframe,title,fun){
  mean=fun
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

@@

plotobs1<-Filtplot1(dfsv1,"Bootstrap Particle Filter SP500",sv_bpf1)
plotobs2<-Filtplot1(dfsv2,"Opt Ker Guided Particle Filter SP500",sv_gpfopt1)
plotobs3<-Filtplot1(dfsv3,"Auxiliary Particle Filter SP500",sv_apf1)
plotobs4<-Filtplot1(dfsv4,"Liu and West Filter SP500",sv_lw1)
plotobs5<-Filtplot1(dfsv5,"Always Resampling SP500",sv_bapf1)
plotobs6<-Filtplot1(dfsv6,"No Resampling SP500",sv_sis1)

@@

Filtplot2<-function(dataframe,title,fun){
  mean=fun
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

@@

plotobs7<-Filtplot2(dfsv7,"Bootstrap Particle Filter STOXX50E",sv_bpf2)
plotobs8<-Filtplot2(dfsv8,"Opt Ker Guided Particle Filter STOXX50E",sv_gpfopt2)
plotobs9<-Filtplot2(dfsv9,"Auxiliary Particle Filter STOXX50E",sv_apf2)
plotobs10<-Filtplot2(dfsv10,"Liu and West Filter STOXX50E",sv_lw2)
plotobs11<-Filtplot2(dfsv11,"Always Resampling STOXX50E",sv_bapf2)
plotobs12<-Filtplot2(dfsv12,"No Resampling STOXX50E",sv_sis2)

@@

Filtplot3<-function(dataframe,title,fun){
  mean=fun
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

@@

plotobs13<-Filtplot3(dfsv13,"Bootstrap Particle Filter DJI",sv_bpf3)
plotobs14<-Filtplot3(dfsv14,"Opt Ker Guided Particle Filter DJI",sv_gpfopt3)
plotobs15<-Filtplot3(dfsv15,"Auxiliary Particle Filter DJI",sv_apf3)
plotobs16<-Filtplot3(dfsv16,"Liu and West Filter DJI",sv_lw3)
plotobs17<-Filtplot3(dfsv17,"Always Resampling DJI",sv_bapf3)
plotobs18<-Filtplot3(dfsv18,"No Resampling DJI",sv_sis3)

@@

Filtplot4<-function(dataframe,title,funmean,funsd){
  mean=funmean
  sd=funsd
  dataframe<-data.frame(dataframe,mean)

@@

plotcomp1<-Filtplot4(dfsv1,"Bootstrap Particle Filter SP500",sv_bpf1,sv_bpf1sd)
plotcomp2<-Filtplot4(dfsv2,"Opt Ker Guided Particle Filter SP500",sv_gpfopt1,sv_gpfopt1sd)
plotcomp3<-Filtplot4(dfsv3,"Auxiliary Particle Filter SP500",sv_apf1,sv_apf1sd)
plotcomp5<-Filtplot4(dfsv5,"Always Resampling SP500",sv_bapf1,sv_bapf1sd)
plotcomp6<-Filtplot4(dfsv6,"No Resampling SP500",sv_sis1,sv_sis1sd)

@@

Filtplot5<-function(dataframe,title,fun,realisedx){
  mean=fun
  mean1=exp(mean/2)
  dataframe<-data.frame(dataframe,mean1)

  ggplot(dataframe,aes(x=timeframe))+
    geom_line(aes(y=realisedx, col="Proxy", linetype="Proxy"))+
    geom_line(aes(y=mean1, col="Filtered Volatility", linetype="Filtered Volatility"))+
    scale_color_manual("",
                       values=c("Proxy" = "black",
                                "Filtered Volatility"= "red"))+
    scale_linetype_manual("",
                          values=c("Proxy" = 3,
                                   "Filtered Volatility"=1))+
    labs(x="Time",
         y="")+
    ggtitle(title)+
    theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
          legend.background = element_rect(fill = "white", colour = "gray30")) +
    theme(plot.title = element_text(hjust = 0.5))
}

plotproxy1<-Filtplot5(dfsv1,"Bootstrap Particle Filter SP500",sv_bpf1,realisedx1)
plotproxy2<-Filtplot5(dfsv2,"Opt Ker Guided Particle Filter SP500",sv_gpfopt1,realisedx1)
plotproxy3<-Filtplot5(dfsv3,"Auxiliary Particle Filter SP500",sv_apf1,realisedx1)
plotproxy4<-Filtplot5(dfsv4,"Liu and West Filter SP500",sv_lw1,realisedx1)
plotproxy5<-Filtplot5(dfsv5,"Always Resampling SP500",sv_bapf1,realisedx1)
plotproxy6<-Filtplot5(dfsv6,"No Resampling SP500",sv_sis1,realisedx1)

@@

plotproxy7<-Filtplot5(dfsv7,"Bootstrap Particle Filter STOXX",sv_bpf2,realisedx2)
plotproxy8<-Filtplot5(dfsv8,"Opt Ker Guided Particle Filter STOXX",sv_gpfopt2,realisedx2)
plotproxy9<-Filtplot5(dfsv9,"Auxiliary Particle Filter STOXX",sv_apf2,realisedx2)
plotproxy10<-Filtplot5(dfsv10,"Liu and West Filter STOXX",sv_lw2,realisedx2)
plotproxy11<-Filtplot5(dfsv11,"Always Resampling STOXX",sv_bapf2,realisedx2)
plotproxy12<-Filtplot5(dfsv12,"No Resampling STOXX",sv_sis2,realisedx2)
